Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex

\subsection{Data Type}
To determine the most concerning and least concerning data types, we consider the very upset rate (VUR) of various scenarios. To calculate these rates, we take the rate of responses where participants had indicated that they would be ``very upset'' (the maximum rating) with respect to the total number of responses for the question. Since people considered different things more or less sensitive with respect to the data recipient, we present the most and least concerning shared data along with the most and least concerning ``not shared'' data:

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
%starting from #63
<data> &  VUR  \\
eye movement patterns (for eye tracking) & 40.51\% \\
when and how much you exercise  & 38.66\% \\
when you are happy or having fun  & 34.51\% \\
which television shows you watch & 30.20\% \\
when you are busy or interruptible  & 29.50\% \\
music from your device  & 28.06\% \\
your heart rate & 27.50\% \\
your age & 24.29\% \\
the language you speak & 15.86\% \\
your gender & 14.91\% \\

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{llll}
Recipients	& Chi^2 &	2-tail P &  Effect Size \\
Work-App	& 564.318 & <0.0001 & 0.111\\
Public-App	& 479.980 & <0.0001 &  0.092\\
Friends-App & 380.000 & <0.0001 & 0.075\\
Friends-Work & 20.365 & <0.0001 &  0.004\\
Friends-Public & 5.349 & 0.0207 &  0.001\\
Work-Public&  5.054 & 0.0246 &  0.001\\
\end{tabular}
\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
\label{recipient}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
<data> & VUR  \\
social security number & 98.04\% \\
a video of you unclothed & 97.44\% \\
bank account information & 97.10\% \\
recordings of your work conversations & 96.97\% \\
an incriminating/embarrassing photo of you & 96.36\% \\
a photo of you unclothed & 96.30\% \\
credit card information & 95.92\% \\
username and password for websites & 95.41\% \\
a video of you entering in your PIN & 93.91\% \\
recordings of your phone conversations & 93.88\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedtop10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
%starting from #63
<data> &  VUR  \\
bank account information & 90.91\% \\
a video of you unclothed & 90.62\% \\
social security number  & 88.68\% \\
video of you entering your PIN & 88.57\% \\
an incriminating/embarrassing photo of you & 78.05\% \\
a photo of you unclothed & 77.78\% \\
a video of you entering a passcode to a door & 75.00\% \\
when and how much you have sex & 73.08\% \\
an incriminating/embarrassing video of you & 71.88\% \\
a random (inward-facing) photo of you at home & 66.67\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedtop10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
%starting from #63
<data> &  VUR  \\
your name & 47.25\% \\
when and how much you exercise & 46.07\% \\
when you were happy or having fun & 38.10\% \\
what television shows you watch & 35.96\% \\
when you are busy or interruptible & 34.34\% \\
your heart rate & 32.28\% \\
music from your device & 31.87\% \\
your age & 29.67\% \\
the language you speak & 20.95\% \\
your gender & 16.81\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedbottom10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
%starting from #63
<data> &  VUR  \\
when and how much you exercise & 16.67\% \\
how much you use your phone & 15.79\% \\
your age & 14.29\% \\
how much you like the people you interact with & 13.79\% \\
when, what, and how much you ate & 12.50\% \\
which television shows you watch & 11.43\% \\
your gender & 9.52\% \\
your heart rate & 9.09\% \\
eye movement patterns (for eye tracking) & 6.98\% \\
the language you speak & 2.50\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedbottom10}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
  (cubetastic upset rate | smartphone upset rate)\\
Q1: (14.81\% | 6.13\%)\\
Q2: (44.11\% | 19.85\%)\\
Q3: (87.09\% | 58.44\%)\\
Q4: (52.77\% | 55.79\%)\\
Q5: (86.49\% | 91.82\%)\\ 
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{deviceVUR}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{llll}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
Question & Chi^2 &	2-tail P & Effect Size\\
All & 2.814 & 0.1395 & 0.001\\
Q1 & 2.500 & 0.1139 & 0.004\\
Q2 & 17.333 & <0.0001 & 0.024\\
Q3 & 0.020 & 0.8886 & 0.000\\
Q4 & 1.426 & 0.2324 & 0.002\\
Q5 & 1.611	 & 0.2043 & 0.002\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
\label{betweendevice}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{llll}
%Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\
%All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
%Q1		0		1		No	n/a	         n/a	                  n/a\\
%Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
%Q3		0		1		No	n/a	         n/a	                  n/a\\
%Q4		0		1		No	0.5		95\%			0.008 to9.605\\
%Q5		0		1		No	n/a	         n/a	                  n/a\\
Question & Chi^2 &	2-tail P & Effect Size \\
All & 0.444  & 0.505 & 0.006\\
Q1 & 0 & 1 & 0 \\
Q2 & 0 & 1 & 0\\
Q3 & 0 & 1 & 0\\
Q4 & 0 & 1 & 0\\
Q5 & 0 & 1 & 0\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
\label{withindevice}
\end{center}
\end{table}

>>>>

\subsection{Data Type}
INTRO HERE.

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
eye movement patterns (for eye tracking) & 40.51\% \\
when and how much you exercise  & 38.66\% \\
when you are happy or having fun  & 34.51\% \\
which television shows you watch & 30.20\% \\
when you are busy or interruptible  & 29.50\% \\
music from your device  & 28.06\% \\
your heart rate & 27.50\% \\
your age & 24.29\% \\
the language you speak & 15.86\% \\
your gender & 14.91\% \\

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
Recipients	& Chi^2 &	2-tail P &  Effect Size \\
Work-App	& 564.318 & <0.0001 & 0.111\\
Public-App	& 479.980 & <0.0001 &  0.092\\
Friends-App & 380.000 & <0.0001 & 0.075\\
Friends-Work & 20.365 & <0.0001 &  0.004\\
Friends-Public & 5.349 & 0.0207 &  0.001\\
Work-Public&  5.054 & 0.0246 &  0.001\\
\end{tabular}
\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
\label{recipient}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
<data> & VUR  \\
social security number & 98.04\% \\
a video of you unclothed & 97.44\% \\
bank account information & 97.10\% \\
recordings of your work conversations & 96.97\% \\
an incriminating/embarrassing photo of you & 96.36\% \\
a photo of you unclothed & 96.30\% \\
credit card information & 95.92\% \\
username and password for websites & 95.41\% \\
a video of you entering in your PIN & 93.91\% \\
recordings of your phone conversations & 93.88\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedtop10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
bank account information & 90.91\% \\
a video of you unclothed & 90.62\% \\
social security number  & 88.68\% \\
video of you entering your PIN & 88.57\% \\
an incriminating/embarrassing photo of you & 78.05\% \\
a photo of you unclothed & 77.78\% \\
a video of you entering a passcode to a door & 75.00\% \\
when and how much you have sex & 73.08\% \\
an incriminating/embarrassing video of you & 71.88\% \\
a random (inward-facing) photo of you at home & 66.67\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedtop10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
your name & 47.25\% \\
when and how much you exercise & 46.07\% \\
when you were happy or having fun & 38.10\% \\
what television shows you watch & 35.96\% \\
when you are busy or interruptible & 34.34\% \\
your heart rate & 32.28\% \\
music from your device & 31.87\% \\
your age & 29.67\% \\
the language you speak & 20.95\% \\
your gender & 16.81\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedbottom10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
when and how much you exercise & 16.67\% \\
how much you use your phone & 15.79\% \\
your age & 14.29\% \\
how much you like the people you interact with & 13.79\% \\
when, what, and how much you ate & 12.50\% \\
which television shows you watch & 11.43\% \\
your gender & 9.52\% \\
your heart rate & 9.09\% \\
eye movement patterns (for eye tracking) & 6.98\% \\
the language you speak & 2.50\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedbottom10}
\end{center}
\end{table}

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c |}
 Question &  Wearable VUR & Smartphone VUR \\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.79\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{deviceVUR}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
Question & Chi^2 &	2-tail P & Effect Size\\
All & 2.814 & 0.1395 & 0.001\\
Q1 & 2.500 & 0.1139 & 0.004\\
Q2 & 17.333 & <0.0001 & 0.024\\
Q3 & 0.020 & 0.8886 & 0.000\\
Q4 & 1.426 & 0.2324 & 0.002\\
Q5 & 1.611 & 0.2043 & 0.002\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
\label{betweendevice}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\
%All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
%Q1		0		1		No	n/a	         n/a	                  n/a\\
%Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
%Q3		0		1		No	n/a	         n/a	                  n/a\\
%Q4		0		1		No	0.5		95\%			0.008 to9.605\\
%Q5		0		1		No	n/a	         n/a	                  n/a\\
Question & Chi^2 &	2-tail P & Effect Size \\
All & 0.444  & 0.505 & 0.006\\
Q1 & 0 & 1 & 0 \\
Q2 & 0 & 1 & 0\\
Q3 & 0 & 1 & 0\\
Q4 & 0 & 1 & 0\\
Q5 & 0 & 1 & 0\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
\label{withindevice}
\end{center}
\end{table}
